Open source landscape ecology tools

### 2020-07-21 paper/paper.Rmd
adds page number

While R has several build-in data structures, including data frames, it has not got any internal support for reading, processing, or visualizing spatial data.
However, there was a notable interest in spatial data analysis since the inception of this language, which is shown in a long R history of packages supporting spatial data (\cite{Lovelace2019}, page ????). <!--history section-->
Comparing to dedicated GIS software (e.g., QGIS, ArcGIS), both raster and vector models have several implementations in the R language.
<!-- are pros/cons of that needed? -->
<!-- info about GDAL/PROJ? -->

@@

## Basic spatial data

>>>>

While R has several build-in data structures, including data frames, it has not got any internal support for reading, processing, or visualizing spatial data.
However, there was a notable interest in spatial data analysis since the inception of this language, which is shown in a long R history of packages supporting spatial data (\cite{Lovelace2019}, page 10). <!--history section-->
Comparing to dedicated GIS software (e.g., QGIS, ArcGIS), both raster and vector models have several implementations in the R language.
<!-- are pros/cons of that needed? -->
<!-- info about GDAL/PROJ? -->

@@

## Spatial data processing
